Meta-analysis of the `ironic' effects of intergroup contact

### 2021-03-22 manuscript/manuscript.Rmd
update posterior predictive simulations

  # Make posterior predictions
  results <- read_rds("../results/results_preregistered_analyses.rds") %>% 
    mutate(
      r_pred_l80 = z_to_r(qnorm(0.10, mu, tau_jj)),
      r_pred_u80 = z_to_r(qnorm(0.90, mu, tau_jj)),
    )

  # Summarise results
  results <- results %>% 
    pivot_longer(
      c(r_mean, tau_ii, tau_jj, r_pred_l80, r_pred_u80),
      names_to = "parameter",
      values_to = "estimate",
      values_drop_na = TRUE
    ) %>% 
    group_by(x_var, y_var, parameter) %>% 
    summarize(
      I = f_comma(unique(I)),
      J = f_comma(unique(J)),
      N = f_comma(unique(N)),
      median = median(estimate),
      .lower = quantile(estimate, 0.025),
      .upper = quantile(estimate, 0.975),
      p_below = mean(estimate < 0),
      p_above = mean(estimate > 0)
    ) %>% 
    ungroup() %>% 
    mutate(
      across(
        c(median, .lower, .upper), 
        ~f_num(., digits = 2)
      ),
      across(
        c(p_below, p_above), 
        ~case_when(
          . < .001 ~ "$<0.1\\%$",
          . > .999 ~ "$>99.9\\%$",
          TRUE ~ paste0("$", f_num(. * 100, digits = 1), "\\%$")
        )
      ),
      text = case_when(
        parameter == "r_mean" ~ paste0("$r = ", median, ", [", .lower, ", ", .upper, "]$"),
        parameter == "tau_ii" ~ paste0("$\\tau_I = ", median, ", [", .lower, ", ", .upper, "]$"),
        parameter == "tau_jj" ~ paste0("$\\tau_J = ", median, ", [", .lower, ", ", .upper, "]$"),
        TRUE ~ paste0("$", median, ", [", .lower, ", ", .upper, "]$")
      )
    ) %>% 
    select(-median, -.lower, -.upper)

@@

  # Summarize predictions for statistical power
  n_req <- read_rds("../results/n_req.rds") %>%
    group_by(y_var) %>%
    summarize(
      across(
        c(n, r),
        list(
          "med" = ~median(.),
          "l95" = ~quantile(., 0.025),
          "u95" = ~quantile(., 0.975)
        )
      )
    ) %>%
    mutate(
      across(starts_with("n"), ~f_comma(ceiling(.))),
      across(starts_with("r"), ~f_num(., digits = 3)),
      n_text = paste0(n_med, ", [", n_l95, ", ", n_u95, "]"),
      r_text = paste0("$|r| > ", r_med, ", [", r_l95, ", ", r_u95, "]$")
    )

@@

*Perceived injustice.* Across `r unique(pi_results$N)` participants from `r unique(pi_results$I)` samples in `r unique(pi_results$J)` studies, we found strong evidence for a weak association (`r pi_results$text[pi_results$parameter == "r_mean"]`) between intergroup contact and perceived injustice, with `r pi_results$p_below[pi_results$parameter == "r_mean"]` of posterior samples for the mean correlation coefficient falling below zero. We found evidence that correlation coefficients varied across studies (`r pi_results$text[pi_results$parameter == "tau_jj"]`) and across samples within studies  (`r pi_results$text[pi_results$parameter == "tau_ii"]`). Based on these analyses, we predicted that 80\% of studies would result in correlation coefficients between `r pi_results$text[pi_results$parameter == "r_pred_l80"]` and `r pi_results$text[pi_results$parameter == "r_pred_u80"]` and that researchers would need sample sizes of at least `r n_req$n_text[n_req$y_var == "pi"]` participants to find significant associations ($\alpha = .05$, two-sided) in 80\% of their studies.^[Sample sizes are based on posterior predictions from the three models, which implied that, for 80\% of studies, the absolute correlation coefficient would be `r n_req$r_text[n_req$y_var == "pi"]` for perceived injustice, `r n_req$r_text[n_req$y_var == "ca"]` for collective action, and `r n_req$r_text[n_req$y_var == "ps"]` for policy support.]

@@

*Collective action.* Across `r unique(ca_results$N)` participants from `r unique(ca_results$I)` samples in `r unique(ca_results$J)` studies, we found some evidence for a weak association (`r ca_results$text[ca_results$parameter == "r_mean"]`) between intergroup contact and collective action, with `r ca_results$p_below[ca_results$parameter == "r_mean"]` of posterior samples for the mean correlation coefficient falling below zero. We found evidence that correlation coefficients varied across studies (`r ca_results$text[ca_results$parameter == "tau_jj"]`) and across samples within studies  (`r ca_results$text[ca_results$parameter == "tau_ii"]`). Based on these analyses, we predicted that 80\% of studies would result in correlation coefficients between `r ca_results$text[pi_results$parameter == "r_pred_l80"]` and `r ca_results$text[pi_results$parameter == "r_pred_u80"]` and that researchers would need sample sizes of at least `r n_req$n_text[n_req$y_var == "ca"]` participants to find significant associations ($\alpha = .05$, two-sided) in 80\% of their studies.

@@

*Policy support.* Across `r unique(ps_results$N)` participants from `r unique(ps_results$I)` samples in `r unique(ps_results$J)` studies, we found some evidence for a weak association (`r ps_results$text[ps_results$parameter == "r_mean"]`) between intergroup contact and policy support, with `r ps_results$p_below[ps_results$parameter == "r_mean"]` of posterior samples for the mean correlation coefficient falling below zero. We found evidence that correlation coefficients varied across studies (`r ps_results$text[ps_results$parameter == "tau_jj"]`) and, to a lesser extent, across samples within studies  (`r ps_results$text[ps_results$parameter == "tau_ii"]`). Based on these analyses, we predicted that 80\% of studies would result in correlation coefficients between `r ps_results$text[pi_results$parameter == "r_pred_l80"]` and `r ps_results$text[pi_results$parameter == "r_pred_u80"]` and that researchers would need sample sizes of at least `r n_req$n_text[n_req$y_var == "ps"]` participants to find significant associations ($\alpha = .05$, two-sided) in 80\% of their studies.

>>>>

  # Summarize results
  results <- read_rds("../results/results_preregistered_analyses.rds") %>% 
    pivot_longer(
      c(r_mean, tau_ii, tau_jj),
      names_to = "parameter",
      values_to = "estimate",
      values_drop_na = TRUE
    ) %>% 
    group_by(x_var, y_var, parameter) %>% 
    summarize(
      I = f_comma(unique(I)),
      J = f_comma(unique(J)),
      N = f_comma(unique(N)),
      median = median(estimate),
      .lower = quantile(estimate, 0.025),
      .upper = quantile(estimate, 0.975),
      p_below = mean(estimate < 0),
      p_above = mean(estimate > 0)
    ) %>% 
    ungroup() %>% 
    mutate(
      across(
        c(median, .lower, .upper), 
        ~f_num(., digits = 2)
      ),
      across(
        c(p_below, p_above), 
        ~case_when(
          . < .001 ~ "$<0.1\\%$",
          . > .999 ~ "$>99.9\\%$",
          TRUE ~ paste0("$", f_num(. * 100, digits = 1), "\\%$")
        )
      ),
      text = case_when(
        parameter == "r_mean" ~ paste0("$r = ", median, ", [", .lower, ", ", .upper, "]$"),
        parameter == "tau_ii" ~ paste0("$\\tau_I = ", median, ", [", .lower, ", ", .upper, "]$"),
        parameter == "tau_jj" ~ paste0("$\\tau_J = ", median, ", [", .lower, ", ", .upper, "]$"),
        TRUE ~ paste0("$", median, ", [", .lower, ", ", .upper, "]$")
      )
    ) %>% 
    select(-median, -.lower, -.upper)

@@

  # Set seed (for posterior predictive simulations)
  set.seed(9071118)

  # Simulate posterior predictions
  post_pred <- read_rds("../results/results_preregistered_analyses.rds") %>% 
    filter(x_var == "ic") %>% 
    mutate(
      r_pred = z_to_r(rnorm(n = n(), mean = mu, sd = tau_jj))
    )

  # Define functions for power calculations
  p_value <- function(r, n) 2*min(pnorm(0, r_to_z(r), 1/sqrt(n - 3)), 1-pnorm(0, r_to_z(r), 1/sqrt(n - 3)))
  p_value <- Vectorize(p_value)
  n_req   <- function(r) uniroot(function(n) ( 0.05 - p_value(r, n) ), c(3, 1e6))$root
  n_req   <- Vectorize(n_req)

  # Summarize posterior predictions
  post_pred <- post_pred %>% 
    group_by(x_var, y_var) %>% 
    summarize(
      r_pred_l80 = quantile(r_pred, 0.10),
      r_pred_u80 = quantile(r_pred, 0.90),
      r_abs = quantile(abs(r_pred), 0.20),
      n_req = n_req(r_abs)
    ) %>% 
    ungroup() %>% 
    mutate(
      across(
        c(r_pred_l80, r_pred_u80),
        ~f_num(., digits = 2)
      ),
      r_abs = paste0("$|r| > ", f_num(r_abs, digits = 3), "$"),
      n_req = f_comma(ceiling(n_req))
    )

@@

*Perceived injustice.* Across `r unique(pi_results$N)` participants from `r unique(pi_results$I)` samples in `r unique(pi_results$J)` studies, we found strong evidence for a weak association (`r pi_results$text[pi_results$parameter == "r_mean"]`) between intergroup contact and perceived injustice, with `r pi_results$p_below[pi_results$parameter == "r_mean"]` of posterior samples for the mean correlation coefficient falling below zero. We found evidence that correlation coefficients varied across studies (`r pi_results$text[pi_results$parameter == "tau_jj"]`) and across samples within studies  (`r pi_results$text[pi_results$parameter == "tau_ii"]`). Based on these analyses, we predicted that 80\% of studies would result in correlation coefficients between `r post_pred$r_pred_l80[post_pred$y_var == "pi"]` and `r post_pred$r_pred_u80[post_pred$y_var == "pi"]` and that researchers would need sample sizes of at least `r post_pred$n_req[post_pred$y_var == "pi"]` participants to find significant associations ($\alpha = .05$, two-sided) in 80\% of their studies.^[Sample sizes are based on posterior predictions from the three models, which implied that, for 80\% of studies, the absolute correlation coefficient would be `r post_pred$r_abs[post_pred$y_var == "pi"]` for perceived injustice, `r post_pred$r_abs[post_pred$y_var == "ca"]` for collective action, and `r post_pred$r_abs[post_pred$y_var == "ps"]` for policy support.]

@@

*Collective action.* Across `r unique(ca_results$N)` participants from `r unique(ca_results$I)` samples in `r unique(ca_results$J)` studies, we found some evidence for a weak association (`r ca_results$text[ca_results$parameter == "r_mean"]`) between intergroup contact and collective action, with `r ca_results$p_below[ca_results$parameter == "r_mean"]` of posterior samples for the mean correlation coefficient falling below zero. We found evidence that correlation coefficients varied across studies (`r ca_results$text[ca_results$parameter == "tau_jj"]`) and across samples within studies  (`r ca_results$text[ca_results$parameter == "tau_ii"]`). Based on these analyses, we predicted that 80\% of studies would result in correlation coefficients between `r post_pred$r_pred_l80[post_pred$y_var == "ca"]` and `r post_pred$r_pred_u80[post_pred$y_var == "ca"]` and that researchers would need sample sizes of at least `r post_pred$n_req[post_pred$y_var == "ca"]` participants to find significant associations ($\alpha = .05$, two-sided) in 80\% of their studies.

@@

*Policy support.* Across `r unique(ps_results$N)` participants from `r unique(ps_results$I)` samples in `r unique(ps_results$J)` studies, we found some evidence for a weak association (`r ps_results$text[ps_results$parameter == "r_mean"]`) between intergroup contact and policy support, with `r ps_results$p_below[ps_results$parameter == "r_mean"]` of posterior samples for the mean correlation coefficient falling below zero. We found evidence that correlation coefficients varied across studies (`r ps_results$text[ps_results$parameter == "tau_jj"]`) and, to a lesser extent, across samples within studies  (`r ps_results$text[ps_results$parameter == "tau_ii"]`). Based on these analyses, we predicted that 80\% of studies would result in correlation coefficients between `r post_pred$r_pred_l80[post_pred$y_var == "ps"]` and `r post_pred$r_pred_u80[post_pred$y_var == "ps"]` and that researchers would need sample sizes of at least `r post_pred$n_req[post_pred$y_var == "ps1"]` participants to find significant associations ($\alpha = .05$, two-sided) in 80\% of their studies.

### 2021-03-22 manuscript/manuscript.tex
update posterior predictive simulations

\emph{Perceived injustice.} Across 201,912 participants from 123 samples
in 84 studies, we found strong evidence for a weak association
(\(r = -.07, [-.10, -.04]\)) between intergroup contact and perceived
injustice, with \(>99.9\%\) of posterior samples for the mean
correlation coefficient falling below zero. We found evidence that
correlation coefficients varied across studies
(\(\tau_J = .14, [.12, .17]\)) and across samples within studies
(\(\tau_I = .08, [.05, .12]\)). Based on these analyses, we predicted
that 80\% of studies would result in correlation coefficients between
\(-.25, [-.30, -.21]\) and \(.11, [.07, .16]\) and that researchers
would need sample sizes of at least 2,299, {[}1,558, 3,295{]}
participants to find significant associations (\(\alpha = .05\),
two-sided) in 80\% of their studies.\footnote{Sample sizes are based on
  posterior predictions from the three models, which implied that, for
  80\% of studies, the absolute correlation coefficient would be
  \(|r| > .041, [.034, .050]\) for perceived injustice,
  \(|r| > .045, [.032, .065]\) for collective action, and
  \(|r| > .036, [.022, .064]\) for policy support.}

\emph{Collective action.} Across 119,085 participants from 37 samples in
24 studies, we found some evidence for a weak association
(\(r = -.06, [-.13, .02]\)) between intergroup contact and collective
action, with \(93.6\%\) of posterior samples for the mean correlation
coefficient falling below zero. We found evidence that correlation
coefficients varied across studies (\(\tau_J = .16, [.12, .23]\)) and
across samples within studies (\(\tau_I = .09, [.06, .14]\)). Based on
these analyses, we predicted that 80\% of studies would result in
correlation coefficients between \(-.26, [-.37, -.18]\) and
\(.15, [.07, .27]\) and that researchers would need sample sizes of at
least 1,925, {[}911, 3,724{]} participants to find significant
associations (\(\alpha = .05\), two-sided) in 80\% of their studies.

\emph{Policy support.} Across 13,703 participants from 19 samples in 14
studies, we found some evidence for a weak association
(\(r = -.07, [-.14, -.00]\)) between intergroup contact and policy
support, with \(98.1\%\) of posterior samples for the mean correlation
coefficient falling below zero. We found evidence that correlation
coefficients varied across studies (\(\tau_J = .10, [.06, .18]\)) and,
to a lesser extent, across samples within studies
(\(\tau_I = .03, [.00, .12]\)). Based on these analyses, we predicted
that 80\% of studies would result in correlation coefficients between
\(-.20, [-.32, -.13]\) and \(.06, [-.02, .18]\) and that researchers
would need sample sizes of at least 2,992, {[}949, 8,077{]} participants
to find significant associations (\(\alpha = .05\), two-sided) in 80\%
of their studies.

>>>>

\emph{Perceived injustice.} Across 201,912 participants from 123 samples
in 84 studies, we found strong evidence for a weak association
(\(r = -.07, [-.10, -.04]\)) between intergroup contact and perceived
injustice, with \(>99.9\%\) of posterior samples for the mean
correlation coefficient falling below zero. We found evidence that
correlation coefficients varied across studies
(\(\tau_J = .14, [.12, .17]\)) and across samples within studies
(\(\tau_I = .08, [.05, .12]\)). Based on these analyses, we predicted
that 80\% of studies would result in correlation coefficients between
-.25 and .11 and that researchers would need sample sizes of at least
2,538 participants to find significant associations (\(\alpha = .05\),
two-sided) in 80\% of their studies.\footnote{Sample sizes are based on
  posterior predictions from the three models, which implied that, for
  80\% of studies, the absolute correlation coefficient would be
  \(|r| > .039\) for perceived injustice, \(|r| > .045\) for collective
  action, and \(|r| > .035\) for policy support.}

\emph{Collective action.} Across 119,085 participants from 37 samples in
24 studies, we found some evidence for a weak association
(\(r = -.06, [-.13, .02]\)) between intergroup contact and collective
action, with \(93.6\%\) of posterior samples for the mean correlation
coefficient falling below zero. We found evidence that correlation
coefficients varied across studies (\(\tau_J = .16, [.12, .23]\)) and
across samples within studies (\(\tau_I = .09, [.06, .14]\)). Based on
these analyses, we predicted that 80\% of studies would result in
correlation coefficients between -.27 and .16 and that researchers would
need sample sizes of at least 1,882 participants to find significant
associations (\(\alpha = .05\), two-sided) in 80\% of their studies.

\emph{Policy support.} Across 13,703 participants from 19 samples in 14
studies, we found some evidence for a weak association
(\(r = -.07, [-.14, -.00]\)) between intergroup contact and policy
support, with \(98.1\%\) of posterior samples for the mean correlation
coefficient falling below zero. We found evidence that correlation
coefficients varied across studies (\(\tau_J = .10, [.06, .18]\)) and,
to a lesser extent, across samples within studies
(\(\tau_I = .03, [.00, .12]\)). Based on these analyses, we predicted
that 80\% of studies would result in correlation coefficients between
-.21 and .07 and that researchers would need sample sizes of at least
3,208 participants to find significant associations (\(\alpha = .05\),
two-sided) in 80\% of their studies.
